Data Preparation, Integration and Cleaning

### 2017-03-09 abbDataPrep_Script.Rmd
rename geo market

  # Add individual classes
  str.data$sub.mrkt <- 'rural'
  str.data$sub.mrkt[str.data$sub.class == 'Middle'] <- 'suburban'
  str.data$sub.mrkt[str.data$sub.class == 'Inner'] <- 'city'
  str.data$sub.mrkt[str.data$suburb %in% core.suburbs] <- 'city-core'
  str.data$sub.mrkt[str.data$beach == 1] <- 'beach'

  # Order the factors properly
  str.data$sub.mrkt <- factor(str.data$sub.mrkt, 
                              levels=c('city-core', 'city', 'suburban', 
                                        'rural', 'beach'))

@@

  # Add individual classes
  ltr.data$sub.mrkt <- 'rural'
  ltr.data$sub.mrkt[ltr.data$sub.class == 'Middle'] <- 'suburban'
  ltr.data$sub.mrkt[ltr.data$sub.class == 'Inner'] <- 'city'
  ltr.data$sub.mrkt[ltr.data$suburb %in% core.suburbs] <- 'city-core'
  ltr.data$sub.mrkt[ltr.data$beach == 1] <- 'beach'

  # Order the factors properly
  ltr.data$sub.mrkt <- factor(ltr.data$sub.mrkt, 
                              levels=c('city-core', 'city', 'suburban', 
                                        'rural', 'beach'))

@@

  str.map <- ggplot() +
    geom_polygon(data=subs, aes(x=long, y=lat, group=group), fill='white', color='grey70') +
    geom_point(data=str.data, aes(x=longitude, y=latitude, color=sub.mrkt), size=.2,
               alpha=.2) +
    scale_color_manual(values=sm.col) +
    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
    xlab('') + ylab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_rect(fill = "white"),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          panel.border = element_rect(colour = "black", fill=NA, size=1)) +
    guides(colour = guide_legend(override.aes = list(size=3,
                                                     alpha=1))) + 
    ggtitle('Short-Term Rental Locations')+
    theme(plot.title = element_text(hjust = 0.5))

@@

  ltr.map <- ggplot() +
    geom_polygon(data=subs, aes(x=long, y=lat, group=group), fill='white', color='grey70') +
    geom_point(data=ltr.data, aes(x=longitude, y=latitude, color=sub.mrkt), size=.1,
               alpha=.1) +
    scale_color_manual(values=sm.col) +
    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
    xlab('') + ylab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_rect(fill = "white"),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          panel.border = element_rect(colour = "black", fill=NA, size=1)) +
    guides(colour = guide_legend(override.aes = list(size=3,
                                                     alpha=1))) + 
    ggtitle('Long-Term Rental Locations')+
    theme(plot.title = element_text(hjust = 0.5))

@@

  strtype.map <- ggplot() +
    geom_bar(data=str.data, aes(x=sub.mrkt, fill=sub.mrkt)) +
    scale_fill_manual(values=sm.col) +
    facet_wrap(~type) +
    ylab('# of Properties\n') + xlab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank()) +
    #ggtitle('Short Term Property Type\nBy Submarket')+
    theme(plot.title = element_text(hjust = 0.5))

@@

  ltrtype.map <- ggplot() +
    geom_bar(data=ltr.data, aes(x=sub.mrkt, fill=sub.mrkt)) +
    scale_fill_manual(values=sm.col) +
    facet_wrap(~type) +
    ylab('# of Properties\n') + xlab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank()) +
    #ggtitle('Long Term Property Type\nBy Submarket')+
    theme(plot.title = element_text(hjust = 0.5))

>>>>

  # Add individual classes
  str.data$geo.mrkt <- 'rural'
  str.data$geo.mrkt[str.data$sub.class == 'Middle'] <- 'suburban'
  str.data$geo.mrkt[str.data$sub.class == 'Inner'] <- 'city'
  str.data$geo.mrkt[str.data$suburb %in% core.suburbs] <- 'city-core'
  str.data$geo.mrkt[str.data$beach == 1] <- 'beach'

  # Order the factors properly
  str.data$geo.mrkt <- factor(str.data$geo.mrkt, 
                              levels=c('city-core', 'city', 'suburban', 
                                        'rural', 'beach'))

@@

  # Add individual classes
  ltr.data$geo.mrkt <- 'rural'
  ltr.data$geo.mrkt[ltr.data$sub.class == 'Middle'] <- 'suburban'
  ltr.data$geo.mrkt[ltr.data$sub.class == 'Inner'] <- 'city'
  ltr.data$geo.mrkt[ltr.data$suburb %in% core.suburbs] <- 'city-core'
  ltr.data$geo.mrkt[ltr.data$beach == 1] <- 'beach'

  # Order the factors properly
  ltr.data$geo.mrkt <- factor(ltr.data$geo.mrkt, 
                              levels=c('city-core', 'city', 'suburban', 
                                        'rural', 'beach'))

@@

  str.map <- ggplot() +
    geom_polygon(data=subs, aes(x=long, y=lat, group=group), fill='white', color='grey70') +
    geom_point(data=str.data, aes(x=longitude, y=latitude, color=geo.mrkt), size=.2,
               alpha=.2) +
    scale_color_manual(values=sm.col) +
    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
    xlab('') + ylab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_rect(fill = "white"),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          panel.border = element_rect(colour = "black", fill=NA, size=1)) +
    guides(colour = guide_legend(override.aes = list(size=3,
                                                     alpha=1))) + 
    ggtitle('Short-Term Rental Locations')+
    theme(plot.title = element_text(hjust = 0.5))

@@

  ltr.map <- ggplot() +
    geom_polygon(data=subs, aes(x=long, y=lat, group=group), fill='white', color='grey70') +
    geom_point(data=ltr.data, aes(x=longitude, y=latitude, color=geo.mrkt), size=.1,
               alpha=.1) +
    scale_color_manual(values=sm.col) +
    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
    xlab('') + ylab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_rect(fill = "white"),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          panel.border = element_rect(colour = "black", fill=NA, size=1)) +
    guides(colour = guide_legend(override.aes = list(size=3,
                                                     alpha=1))) + 
    ggtitle('Long-Term Rental Locations')+
    theme(plot.title = element_text(hjust = 0.5))

@@

  strtype.map <- ggplot() +
    geom_bar(data=str.data, aes(x=geo.mrkt, fill=geo.mrkt)) +
    scale_fill_manual(values=sm.col) +
    facet_wrap(~type) +
    ylab('# of Properties\n') + xlab('')+
    theme(legend.position = 'bottom',gc()
          legend.title = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank()) +
    #ggtitle('Short Term Property Type\nBy Submarket')+
    theme(plot.title = element_text(hjust = 0.5))

@@

  ltrtype.map <- ggplot() +
    geom_bar(data=ltr.data, aes(x=geo.mrkt, fill=geo.mrkt)) +
    scale_fill_manual(values=sm.col) +
    facet_wrap(~type) +
    ylab('# of Properties\n') + xlab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank()) +
    #ggtitle('Long Term Property Type\nBy Submarket')+
    theme(plot.title = element_text(hjust = 0.5))
